### 2021-06-05 paper/report.tex
Restore version that runs through without some of Klaras changes.

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/share_of_educ_participants_with_rapid_test}

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/share_of_workers_with_rapid_test_offer_at_work}
        % fraction of workers must be multiplied with 0.6 because only that many actually
        % accept the offer

@@

        Number of PCR tests

>>>>

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/rapid_test_demand_shares}

@@

        \textcolor{red}{Number of PCR tests}
